### 2025-12-03 download-football-data.qmd
20251203 - use nfl4th data on OSF if errors out upon load

```{r}
#| output: false

@@

>>>>

@@

tryCatch(
  {
    nfl_4thdown_raw <- nfl4th::load_4th_pbp(
      seasons = 2014:nflreadr::most_recent_season()
    )
  },
  error = function(e) { # if errors out when trying to load the data using nfl4th::load_4th_pbp()
    message("Primary load failed; falling back to OSF version...")
    petersenlab::robust_load("https://osf.io/download/nhcrj/")
  }
)
```
